### 2021-10-20 paper/paper.tex
tests are only as good as argument values you choose

>>>>

\vskip 6pt
A weakness of \cit is that your tests are only as good as the argument values you choose. Even if you choose argument values such that some combination of them would find a failure, it's possible that the subset of test cases generated by the \cit might not include that combination. There is no guarantee that using automated testing to generate hundreds of tests will find a problem.
